Preregistered as Code: Gender differences in Machiavellianism

### 2021-08-09 README.Rmd
add link to zenodo for preregistration closes #196

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

>>>>

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

Preregistration as Code: [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5170740.svg)](https://doi.org/10.5281/zenodo.5170740)

Results after Preregistration: [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5171678.svg)](https://doi.org/10.5281/zenodo.5171678)

<!-- badges: end -->
